# Author manifest for scripts

## In VSCode:

Open Command Palette: `Ctrl+Shift+P` → `Preferences: Configure User Snippets`
Choose `New Global Snippets` file, e.g. `jyotirmoy-manifestation-snippets.code-snippets`

Add this - 

```{json}
{
"Manifestation + Author Block": {
  "prefix": "authorblock",
  "body": [
    "# Author details",
    "## Script name: $TM_FILENAME",
    "## Purpose of the script: ",
    "## Author(s): Jyotirmoy Das, Ph.D.",
    "## Date Created: ${CURRENT_YEAR}-${CURRENT_MONTH}-${CURRENT_DATE}",
    "## Date Last Modified: ${CURRENT_YEAR}-${CURRENT_MONTH}-${CURRENT_DATE}",
    "## Copyright statement: GNU3 open license",
    "## Contact information: jyotirmoy.das@liu.se",
    "## Please cite:",
    "## @article{}",
    "## Notes:",
    "## Please read the manual/tutorial file for the sample preparation of the analysis.",
    "",
    "$0"
  ],
  "description": "Insert manifestation + author block"
}

  }
  
```

## Git Hook - Pre-commit: Add Block If Missing

Here’s a Git pre-commit hook that adds your manifestation block to new .py, .sh, or .R files that don’t already have it:

📁 Create: .git/hooks/pre-commit

```{bash}
#!/bin/bash

MANIFEST=$(cat <<EOF
# 🌟 Manifestation Block
# Today I create with clarity and purpose.
# This script is aligned with my highest intentions.
# I trust the process and learn through the journey.

EOF
)

for file in $(git diff --cached --name-only --diff-filter=AC | grep -E '\.(py|sh|R)$'); do
  if ! grep -q "🌟 Manifestation Block" "$file"; then
    echo "$MANIFEST$(cat "$file")" > "$file"
    git add "$file"  # re-add updated file
    echo "Manifestation block added to $file"
  fi
done

```

Make it executable `chmod +x .git/hooks/pre-commit`

🔧 If you want it system-wide (for all your repos):
You can use a global Git template directory:

Step-by-step:

# 1. Create a central template directory
mkdir -p ~/.git-template/hooks

# 2. Move your hook there
cp your_repo/.git/hooks/pre-commit ~/.git-template/hooks/pre-commit
chmod +x ~/.git-template/hooks/pre-commit

# 3. Tell Git to use it globally
git config --global init.templateDir '~/.git-template'
Now every time you create a new repo, Git will copy this hook into .git/hooks/.

✅ Bonus: Apply hook to existing repos
You can manually copy the hook:

cp ~/.git-template/hooks/pre-commit /your/old/repo/.git/hooks/pre-commit
Or automate it across multiple repositories with a loop — I can help with that if needed.



## In RStudio:
RStudio Addin for Manifestation Block

Since snippets are tricky in RStudio (especially multi-line), a custom R Addin is the best solution.

🔧 Step-by-step Setup
### ✅ A. Create a New R Package for Addins


`usethis::create_package("~/jyotirmoymanifest")`

Inside that folder, run:

`usethis::use_r("insert_manifestation")`

Paste this function:
```{r}
#| eval: false
#| echo: true
#| code-fold: true
#| title: insertion of manifest
#' Insert Manifestation Header
#' @param filename Optional script name (default uses current file)
#' @export
insert_manifestation <- function(filename = NULL) {
  if (!rstudioapi::hasFun("getActiveDocumentContext")) {
    stop("This function requires RStudio.")
  }

  ctx <- rstudioapi::getActiveDocumentContext()

  # If filename not provided, infer from the open document path
  if (is.null(filename)) {
    filename <- basename(ctx$path)
    if (filename == "") filename <- "new_script.R"
  }

  date <- format(Sys.Date(), "%Y-%m-%d")

  block <- c(
    "# Author details",
    paste0("## Script name: ", filename),
    "## Purpose of the script: ",
    "## Author(s): Jyotirmoy Das, Ph.D.",
    paste("## Date Created:", date),
    paste("## Date Last Modified:", date),
    "## Copyright statement: GNU3 open license",
    "## Contact information: jyotirmoy.das@liu.se",
    "## Please cite:",
    "## @article{}",
    "## Notes:",
    "## Please read the manual/tutorial file for the sample preparation of the analysis.",
    ""
  )

  rstudioapi::insertText(paste(block, collapse = "\n"))
}


```

### ✅ B. Register as an Addin

```{r}
#| eval: false
#| echo: true
#| code-fold: true
#| title: insertion of manifest dcf

dir.create("inst/rstudio", recursive = TRUE)
file.create("inst/rstudio/addins.dcf")

```

Add this to `inst/rstudio/addins.dcf`:

```{text}
Name: Insert Manifestation Header
Description: Insert manifestation + author header at cursor position
Binding: insert_manifestation
Interactive: false
```

### ✅ C. Install Your Addin

In the package root:

```{r}
#| eval: false
#| echo: true
#| code-fold: true
#| title: insertion of manifest install

devtools::document()
devtools::install()
```

### Restart Rstudio and add addin

```{r}
#| eval: false
#| echo: true
#| code-fold: true
#| title: insertion of manifest add

## REMEMBER to add this at the top of the code file - <code-file>.R
library(jyotirmoymanifest)
insert_manifestation()

#or
jyotirmoymanifest::insert_manifestation()

```

::: {.callout-important title="Added in shortcut" collapse="false"}
**And in RStudio:**

- Check the `“Addins”` menu → `Insert Manifestation Header`
- Or assign a shortcut via: `Tools` → `Modify Keyboard Shortcuts`

1. Added to - `ctrl+shift+A` [**Nautilus**]

**Update the package -**
```{r}
#| eval: false
#| echo: true
#| code-fold: true
#| title: update package
setwd("~/jyotirmoymanifest")
devtools::document()
devtools::install()
```

To register the license properly, you can run:

usethis::use_gpl3_license("Jyotirmoy Das")
Or switch to MIT if you want more permissive usage:

usethis::use_mit_license("Jyotirmoy Das")
This will also generate a LICENSE file.


::: {.callout-warning title="tag versions"}
git tag -a v0.1.0 -m "Initial release of manifestation addin"
git push origin v0.1.0

:::

